\huge{Meta-analytic evidence that sexual selection improves population fitness}

### 2019-04-06 Manuscripts/Manuscript_MetaAnalysis.Rmd
Author Contributions changed

#Author contributions  
All authors designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; and all authors contributed substantially to all further revisions.  \phantomsection

>>>>

#Author contributions  
JGC, DSF and LH designed the study; JGC collected the data; JGC and LH conducted the meta-analyses; JGC wrote the first draft of the manuscript; JGC, DSF and LH contributed substantially to all further revisions.  \phantomsection
